Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-22 outputs/paper/paper.qmd
Edits
edits

In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022]. Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,125 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022; @macrotrends].
,
There are many factors that contribute to the increase in hate crimes in Canada. However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada. These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity. Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets on anti-refugee sentiments. A 2021 paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research [@main_paper].
=======
In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022]. Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 [@government_of_canada_2022] and 130,125 refugees in 2020 [@macrotrends], these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents.

There are many factors that contribute to the increase in hate crimes in Canada. However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada. These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity. Despite this, one factor that has received little attention until recently is the impact of mate competition in dating and marriage markets on anti-refugee sentiments. A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this potentially important and often-overlooked fusion of social science with ecology.
>>>>>>> bca9bbc77a3d3c7b3af7a6d9319550b759e6f77f

In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper]. This population of individuals, non-immigrant German males in highly male populated municipalities being the estimand of the study. Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper]. Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper].

In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper]. This population of individuals, non-immigrant German males in highly male populated municipalities being the estimand of the study. Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper]. Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper].

Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence. Our paper seeks to replicate their two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians. Our reproduction was conducted using the statistical programming language R [@citeR]. To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [@sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr], kableExtra, [@kableExtra].

We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction. We will then conduct a reproduction of their results to better improve upon the accessibility of their findings. Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.

@@

This paper will replicate the survey data that was originally collected for the 2021 paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned. Using the online survey platform "Respondi", they conduct four waves of surveys which spanned from September 2016 to December 2017 [@main_paper]. The researchers suggest that the anonymity provided by the online survey platform resulted in respondents answering more truthfully. [@main_paper]. To mitigate potential biases, the researchers employed list experiments in Waves 1 and 2, and in Wave 2, they randomly assigned 50% of the sample to either a control or treatment group. The treatment group was exposed to statements concerning their agreement with using violence against refugees as a means to get the attention of German politicians. However, no evidence was found to suggest that respondents were concealing their support for hate crimes when comparing the means of the control and treatment groups [@main_paper].

@@

The original survey data assessed participants on 53 variables, being representative of gender, age and state. The range of recorded age data from the survey occurs from 19-89 years old. Age was then categorized by group which is as follows: 18-29, 30-39, 30-49, 50-59, and 60 and older. Both male and female participants took part in the survey, but females were only involved in the second and fourth waves of surveys. The survey was distributed across 16 German states. Our reproduction, however, included removing variables that were not utilized in our final reproduction analysis and included only the necessary Waves 2 and 4. As a part of our reproduction, we also simplified the names of variables to make them easier to work with. From the original survey data, each variable correlates with a survey question asked to participants. To discuss the variables used in our reproduction we have grouped them in the following way and have listed each variable below.

@@

-   Age Group
-   Gender
-   State
-   German Citizen
-   Marital Status
-   Relationship status, single
-   Religious Affiliation
-   Education
-   Occupation
-   Income
-   Household Size
-   Subjective Social Status
-   Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality
-   Politics: left and right-leaning
-   Politics: affiliated parties

[Mate Competition: using a scale of agree or disagree]{.underline}

-   The influx of male refugees make it difficult for non-immigrant German men to find female partners
-   Job Competition: using a scale of agree or disagree
-   The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs

@@

-   Satisfaction with life

@@

-   How many KM is the closest refugee reception center from your home

-   How many refugees do you believe have settled in your municipality in the last year

-   In the last month, how many refugees have you encountered in the following locations

@@

-   Violence is sometimes the only means that citizens have to get the attention of German politicians - Attitudes towards Muslims

-   Hostility against refugees is justified

-   Politicians should condemn attacks against refugees

-   Racist violence is defensible if it leads to fewer refugees settling in a town

-   Attacks against refugee homes are sometimes necessary to make garner the attention of politicians

-   Refugees are integrating well into Germany

-   German refugees should be entitled to German citizenship

-   The number of refugees should be reduced

-   Refugees are receiving more than non-immigrant Germans

-   Refugees should give up their culture to adopt that of Germany

-   Refugees are good for the economy

-   Refugees increase crime

-   Increased refugees increase the risk of terrorism

-   Will additional refugees in your town increase the influence of Islam (local)

-   Will additional refugees in your town be a challenge for local schools (local)

-   Will additional refugees in your town increase competition for housing (local)

-   Will additional refugees in your town change the way of life in your town (local)

@@

-   Experiment lists

-   Treatment lists

-   Outcome lists

-   Waves: out of 4

@@

Data from the 4th Wave of surveys were used to show correlation between someone answering that they perceive refugees as a threat to finding a romantic partner and that person's gender, age, and their municipality's gender ratio. We reconstructed the portion of the survey data used for this analysis in @fig-excess, changing the presentation to a comparative bar chart where we can directly, visually compare different categories' response patterns along a consistent y-axis.

@main_paper provides groupings for the varying elements that we wanted to distinguish and compare. The three age/gender groups compared are 1) All (men and women of all ages), 2) Men between ages of 18-44, and 3) Men of "mating age" (30-40), making them of an age that is most commonly seen as the range that people seek to find a partner and "settle down." There were also 3 different groupings for categorizing a municipality's gender ratio which are referred to as "Terciles." Gender ratio was calculated by dividing the male population by the female population of a given municipality [@main_paper]. Within the survey data, each response had a value for that respondents' municipality's gender ratio. @tbl-terc shows the exact value of ratio used to divide groupings into 1st, 2nd, and 3rd Terciles.

Returning to @fig-excess, we immediately notice that the highest rate of perceiving refugees as threats, over 46%, is found in mating-aged men living in municipalities with relatively high male-to-female ratio (at least 1.12 men per 1 woman). Second is men ages 18-44 in the same tercile of municipalities at around 37%. This is in stark contrast to the All group which includes men and women of all ages, where the proportion is lowest in the 1st tercile at around 17%, and highest at the 3rd tercile with 23%. There is one exception of Men 30-40 in the 1st tercile, but otherwise, Men are consistently more likely to perceive refugees as threats to mating than the general population. This jumps greatly the higher the male-to-female ratio is in their own town; the rate in Men 30-40 is almost triple more in the 3rd tercile than the 1st, and about 1.8 times more than the 2nd.

In analyzing @fig-excess, we can recognize that the combination of a person being a man, especially between the ages of 30-40, and living in a municipality that has about 9 men per 8 women does seem to predict a higher rate of that person believing that refugees are negatively affecting their chance at finding a romantic partner. To confirm, it is not necessarily true that these respondents are living in an area with disproportionately more refugee men, but men in general. Yet, there being more men at all in their town leads to them displacing blame on refugees when presented with a question regarding the topic.

@@

Finally, we reconstructed @main_paper's battery of linear models to predict respondents' sentiments toward refugee-directed hate crime. 6 Models were trained with increasing numbers of factors weighted using Ordinary Least Squares @tbl-hatemodel. The first model used solely mate competition (measured by proportion of excess males). Our models grew in complexity such that the second version was inclusive of job competition and life satisfaction. In the next four models, one at a time, sociodemographic factors, attitudes toward refugees (local first, then national), and last, additional factors (including perceptions of refugee settlements and political groups, and their affiliations) were added. Despite the addition of additional factors, across all models, the predictive weight of mate competition remains high. Job competition, on the other hand, was introduced in model 2 with larger weight than mate competition, but it rapidly fell off with the introduction of more factors. Life satisfaction's weight remains low across all inclusive models. Increasing R Squared indicates that model fit increases with additional factors in our model. These findings are consistent with @main_paper.

@@

To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females. Alberta is a Province in Canada with a total population of 4,543,111 individuals. It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females [@statista]. Thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1. This means that there are about 11,000 more men than women residing in this Province. Part of the population gap can be explained by age. Alberta has a primarily young population and we typically see that as populations age they exhibit a higher female population [@edmonton_journal]. Its trades centric economy also attracts young male migrants from across Canada [@edmonton_journal]. Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of males and females [@edmonton_journal]. However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan]. Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe males facing higher tensions of dating competition. We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1. While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence. However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta. Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023]. While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal]. According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants [@globe_mail]. However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees [@globe_mail]. 48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail]. The globe and mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper]. Based on these statistics, we believe that Alberta may experience a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population. However, as stated in their original paper, we call for further research to be conducted on this effect to better understand its implications on non-German countries.

@@

Ethical implications and biases arise naturally when collecting quantitative and qualitative data. In their paper, Dancygier, Egami, Jamal, and Rischke use online survey platforms to assess if Germans living in areas with greater populations of men who experience turmoil in the mating market are more likely to perceive competition between themselves and refugees, moreover, does this ideology predict hate crime support [@main_paper]. The authors attempted to address ethical concerns and statistical biases by utilizing control groups and replicating their study with different samples and polling firms. However, one potential bias that is challenging to control for is the presence of sampling bias [@main_paper]. Sampling bias occurs when participants in a study are not representative of the estimand or the ideal population of interest. One method to control for this bias is simple random sampling, where participants are chosen by chance. Meaning that every individual in the population has an equal chance of being selected. However, in their study, they were unable to utilize simple random sampling. Instead attempted to make their survey results representative by conducting four waves of surveys meant to be representative of age, gender and geographical region [@main_paper]. Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].

@@

Being a reproduction, much of our analysis was limited to the original survey circumstances captured in [@main_paper]. Despite the survey being long, it can not be considered to be comprehensive. This prevented us from exploring other relationships in the data. For example, in this German context, it would have been interesting to look into sentiments toward the treatment of communities experiencing genocide during the history of World War II. Our connection of findings to the Albertan context was also limited by this cultural and geographical separation from our data.

>>>>

In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022]. Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 [@government_of_canada_2022] and 130,125 refugees in 2020 [@macrotrends], these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents.

There are many factors that contribute to the increase in hate crimes in Canada. However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada. These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity. Despite this, one factor that has received little attention until recently is the impact of mate competition in dating and marriage markets on anti-refugee sentiments. A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this potentially important and often-overlooked fusion of social science with ecology.

In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper]. The study population is primarily non-immigrant German males in highly male populated municipalities. The estimand which we intend to replicate is the effect of mate competition on anti-refugee sentiments. Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper]. Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper].

Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence. Our paper seeks to replicate their two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians. Our reproduction was conducted using the statistical programming language R [@citeR]. To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [@sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr] and kableExtra [@kableExtra].

We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction. We will then conduct a reproduction of select results to verify their findings and improve upon their accessibility. Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.

@@

This paper will replicate the survey data that was originally collected for the [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned. Using the online survey platform "Respondi", they conduct 4 waves of surveys which spanned from September 2016 to December 2017 [@main_paper]. The researchers suggest that the anonymity provided by the online survey platform resulted in respondents answering more truthfully. [@main_paper]. To mitigate potential biases, the researchers employed list experiments in Waves 1 and 2, and in Wave 2, they randomly assigned 50% of the sample to either a control or treatment group. The treatment group was exposed to statements concerning their agreement with using violence against refugees as a means to get the attention of German politicians. However, no evidence was found to suggest that respondents were concealing their support for hate crimes when comparing the means of the control and treatment groups [@main_paper].

@@

The original survey data assessed participants on 53 variables, being representative of gender, age and state. The range of recorded age data from the survey occurs from 19-89 years old. Age was then categorized by group which is as follows: 18-29, 30-39, 30-49, 50-59, and 60 and older. Both male and female participants took part in the survey, but females were only involved in Waves 2 and 4 of surveys. The survey was distributed across 16 German states. Our reproduction, however, included removing variables that were not utilized in our final reproduction analysis and included only the necessary Waves 2 and 4. As a part of our reproduction, we also simplified the names of variables to make them easier to work with. From the original survey data, each variable correlates with a survey question asked to participants. To discuss the variables used in our reproduction we have grouped them by category way and have listed each variable below. Some survey questions are presented, and have been reworded slightly for consistency and clarity.

@@

-   Age Group
-   Gender
-   State
-   German Citizen
-   Marital Status
-   Relationship status, single
-   Religious Affiliation
-   Education
-   Occupation
-   Income
-   Household Size
-   Subjective Social Status
-   Excess males: The proportion of males to females by states by dividing the number of women by men aged 14 and 44 for each municipality 
-   Politics: left and right-leaning
-   Politics: affiliated parties

[Mate Competition: using a scale (1-4) to indicate agreement or disagreement]{.underline}

-   The influx of male refugees make it difficult for non-immigrant German men to find female partners

[Job Competition: using a scale of agree or disagree]{.underline}

-   The inflow of young male refugees makes it more difficult for young non-immigrant German men to find work/ jobs

@@

-   Rank your satisfaction with life

@@

-   How many KM is the closest refugee reception center from your home?
-   How many refugees do you believe have settled in your municipality in the last year?
-   In the last month, how many refugees have you encountered in the following locations? (on the street, on public transport or in parks, in stores, in refugee reception centres or hostels, school, work)

@@

-   Violence is sometimes the only means that citizens have to get the attention of German politicians 
-   Attitudes towards Muslims
-   Hostility against refugees is justified
-   Politicians should condemn attacks against refugees
-   Racist violence is defensible if it leads to fewer refugees settling in a town
-   Attacks against refugee homes are sometimes necessary to make garner the attention of politicians
-   Refugees are integrating well into Germany
-   German refugees should be entitled to German citizenship
-   The number of refugees should be reduced
-   Refugees are receiving more than non-immigrant Germans
-   Refugees should give up their culture to adopt that of Germany
-   Refugees are good for the economy
-   Refugees increase crime
-   Increased refugees increase the risk of terrorism
-   Additional refugees in your town will increase the influence of Islam (local)
-   Additional refugees in your town will be a challenge for local schools (local)
-   Additional refugees in your town will increase competition for housing (local)
-   Additional refugees in your town will change the way of life in your town (local)

@@

-   Experiment lists
-   Treatment lists
-   Outcome lists
-   Waves: out of 4

@@

Data from Wave 4 of surveys were used to show correlation between someone answering that they perceive refugees as a threat to finding a romantic partner and that person's gender, age, and their municipality's gender ratio. We reconstructed the portion of the survey data used for this analysis in @fig-excess, changing the presentation to a comparative bar chart where we can directly, visually compare different categories' response patterns along a consistent y-axis.

@main_paper provides groupings for the varying elements that we wanted to distinguish and compare. The three age/gender groups compared are: (1) All (men and women of all ages), (2) Men between ages of 18-44, and (3) Men of "mating age" (30-40), making them of an age that is most commonly seen as the range that people seek to find a partner and "settle down." There were also 3 different groupings for categorizing a municipality's gender ratio which are referred to as "terciles." Gender ratio was calculated by dividing the male population by the female population of a given municipality [@main_paper]. Within the survey data, each response had a value for that respondents' municipality's gender ratio. @tbl-terc shows the exact value of ratio used to divide groupings into 1st, 2nd, and 3rd terciles.

Returning to @fig-excess, we immediately notice that the highest rate of perceiving refugees as threats, over 46%, is found in mating-aged men living in municipalities with relatively high male-to-female ratio (at least 1.12 men per 1 woman). Next is Men ages 18-44 in the same tercile of municipalities at around 37%. This is in stark contrast to the All group which includes men and women of all ages, where the proportion is lowest in the 1st tercile at around 17%, and highest at the 3rd tercile with 23%. There is one exception of Men 30-40 in the 1st tercile, but otherwise, Men are consistently more likely to perceive refugees as threats to mating than the general population. This jumps greatly the higher the male-to-female ratio is in their own town; the rate in Men 30-40 is almost tripled in the 3rd tercile than the 1st, and about 1.8 times more than the 2nd.

In analyzing @fig-excess, we can recognize that the combination of a person being a man, especially between the ages of 30-40, and living in a municipality that has about 9 men per 8 women does seem to predict a higher rate of that person believing that refugees are negatively affecting their chance at finding a romantic partner. To confirm, it is not necessarily true that these respondents are living in an area with disproportionately more refugee men, but men in general. Yet, there being more men at all in their town might lead them to project blame onto refugees when presented with a question regarding the topic.

@@

Finally, we reconstructed @main_paper's battery of linear models to predict respondents' sentiments toward refugee-directed hate crime. 6 Models were trained with increasing numbers of factors weighted using Ordinary Least Squares @tbl-hatemodel. The first model used solely mate competition (measured by proportion of excess males). Our models grew in complexity such that the second version was inclusive of job competition and life satisfaction. In the next four models, one at a time, sociodemographic factors, attitudes toward refugees (local first, then national), and last, additional factors (including perceptions of refugee settlements and political groups, and their affiliations) were added. Despite the addition of factors, across all models, the predictive weight of mate competition remains high. Job competition, on the other hand, was introduced in model 2 with larger weight than mate competition, but it rapidly fell off with the introduction of more factors. Life satisfaction's weight remains low across all inclusive models. Increasing R Squared indicates that model fit increases with additional factors in our model. These findings are consistent with @main_paper.

@@

To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females.

Alberta is a Province in Canada with a total population of 4,543,111 individuals. It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females [@statista]. Thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1. This means that there are about 11,000 more men than women residing in this Province. Part of the population gap can be explained by age. Alberta has a primarily young population and we typically see that as populations age they exhibit a higher female population [@edmonton_journal]. Its trades centric economy also attracts young male migrants from across Canada [@edmonton_journal].

Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of males and females [@edmonton_journal]. However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan]. Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe males facing higher tensions of dating competition. We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.

While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence. However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta. Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023].

While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal]. According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants [@globe_mail]. However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees [@globe_mail]. 48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail]. The Globe and Mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].

Based on these statistics, we believe that Alberta may experience a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population. However, as stated in their original paper, we call for further research to be conducted on this effect to better understand its implications on non-German countries.

@@

Ethical implications and biases arise naturally when collecting quantitative and qualitative data. In their paper, Dancygier, Egami, Jamal, and Rischke use online survey platforms to assess if Germans living in areas with greater populations of men who experience turmoil in the mating market are more likely to perceive competition between themselves and refugees, moreover, does this ideology predict hate crime support [@main_paper]. The authors attempted to address ethical concerns and statistical biases by utilizing control groups and replicating their study with different samples and polling firms. However, one potential bias that is challenging to control for is the presence of sampling bias [@main_paper]. Sampling bias occurs when participants in a study are not representative of the estimand or the ideal population of interest. One method to control for this bias is simple random sampling, where participants are chosen by chance. Meaning that every individual in the population has an equal chance of being selected. However, in their study, they were unable to utilize simple random sampling. Instead attempted to make their survey results representative by conducting 4 waves of surveys meant to be representative of age, gender and geographical region [@main_paper]. Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].

@@

Being a reproduction, much of our analysis was limited to the original survey circumstances captured in [@main_paper]. Despite the survey being long, it can not be considered to be comprehensive. This prevented us from exploring other relationships in the data. For example, in this German context, it would have been interesting to look into sentiments toward the treatment of communities experiencing genocide during the history of World War 2. Our connection of findings to the Albertan context was also limited by this cultural and geographical separation from our data.
